COVID-19 Policy-Compliance in Europe

### 2020-12-24 Draft.Rmd
Trying to get automatic and nice regression table output with texreg, however this needs improvement

```{r libraries, include=FALSE}
# Loading the libraries ----
library(dplyr)
library(ggplot2)
library(scales)
library(lme4)
library(broom.mixed)
library(plotly)
library(reshape2)
library(utils)
```

@@

>>>>

```{r libraries, include=FALSE}
# Loading the libraries ----
library(dplyr)
library(ggplot2)
library(scales)
library(lme4)
library(broom.mixed)
library(plotly)
library(reshape2)
library(utils)
library(texreg)
library(stargazer)
```

@@

```{r echo=FALSE, results="asis"}

report_regression <- function(model, ...){
  if(knitr::is_html_output()){
    require(texreg)
    htmlreg(model, custom.note="%stars. htmlreg", ...)
  } else if(knitr::is_latex_output()){
    require(stargazer)
    stargazer(model, notes="stargazer html", ...)
  } else {
   print("This only works with latex and html output") 
  }
}

lm1 <- lm(data = data, ComplianceIndex ~ Date + Publicity + notification_rate_per_100000_population_14.days + CountryName)

report_regression(lm1)
```
